The sound of teaching music: Expert pianists' performance modulations for novices

### 2022-07-27 paper/manuscript.Rmd
edit .gitignore
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
add additional analysis for dynamics difference
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

>>>>

# Additional analysis for dynamics difference
## Experiment 1
```{r additional-dynamics-1, include = FALSE}
source(here("experiment-1/analysis/stats", "dynamics.R"), chdir = TRUE)
```

A two-way repeated-measures ANOVA with the factors Condition (teaching vs. performing) and Transition Type (FtoP vs. PtoF) showed that there was a significant main effect of Transition Type (*F*(`r vel_diff_dyn_aov_3$anova_table[2,1]`,`r vel_diff_dyn_aov_3$anova_table[2,2]`) = `r sprintf('%.0f', vel_diff_dyn_aov_3$anova_table[2,4])`, *p* `r if(vel_diff_dyn_aov_3$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', vel_diff_dyn_aov_3$anova_table[2,5])`) and a significant interaction between Condition and Transition Type (*F*(`r vel_diff_dyn_aov_3$anova_table[3,1]`,`r vel_diff_dyn_aov_3$anova_table[3,2]`) = `r sprintf('%.2f', vel_diff_dyn_aov_3$anova_table[3,4])`, *p* `r if(vel_diff_dyn_aov_3$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[3,5])`, *Fig TBC*). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there was no significant difference when changing from forte to piano (*p* `r if(vel_diff_dyn_posthoc_2$p.value[1] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_posthoc_2$p.value[1]))}`) and from piano to forte (*p* `r if(vel_diff_dyn_posthoc_2$p.value[2] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_posthoc_2$p.value[2]))}`) between the teaching condition [FtoP: *M* = `r vel_diff_dyn_normalised_all[Condition == "teaching" & Subcomponent == "FtoP"]$Mean`, *SD* = `r vel_diff_dyn_normalised_all[Condition == "teaching" & Subcomponent == "FtoP"]$SD`, PtoF: *M* = `r vel_diff_dyn_normalised_all[Condition == "teaching" & Subcomponent == "PtoF"]$Mean`, *SD* = `r vel_diff_dyn_normalised_all[Condition == "teaching" & Subcomponent == "PtoF"]$SD`] and the performing condition [FtoP: *M* = `r vel_diff_dyn_normalised_all[Condition == "performing" & Subcomponent == "FtoP"]$Mean`, *SD* = `r vel_diff_dyn_normalised_all[Condition == "performing" & Subcomponent == "FtoP"]$SD`, PtoF: *M* = `r vel_diff_dyn_normalised_all[Condition == "performing" & Subcomponent == "PtoF"]$Mean`, *SD* = `r vel_diff_dyn_normalised_all[Condition == "performing" & Subcomponent == "PtoF"]$SD`].

## Experiment 2
```{r additional-dynamics-2, include = FALSE}
source(here("experiment-2/analysis/stats", "dynamics.R"), chdir = TRUE)
```

A two-way repeated-measures ANOVA with the factors Condition (teaching vs. performing) and Transition Type (FtoP vs. PtoF) showed that there was a significant main effect of Transition Type (*F*(`r vel_diff_dyn_aov_3$anova_table[2,1]`,`r vel_diff_dyn_aov_3$anova_table[2,2]`) = `r sprintf('%.0f', vel_diff_dyn_aov_3$anova_table[2,4])`, *p* `r if(vel_diff_dyn_aov_3$anova_table[2,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[2,6]))}`, $\eta_G^2$ = `r sprintf('%.2f', vel_diff_dyn_aov_3$anova_table[2,5])`). However, there was no significant interaction between Condition and Transition Type (*F*(`r vel_diff_dyn_aov_3$anova_table[3,1]`,`r vel_diff_dyn_aov_3$anova_table[3,2]`) = `r sprintf('%.2f', vel_diff_dyn_aov_3$anova_table[3,4])`, *p* `r if(vel_diff_dyn_aov_3$anova_table[3,6] < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[3,6]))}`, $\eta_G^2$ = `r sprintf('%.3f', vel_diff_dyn_aov_3$anova_table[3,5])`, *Fig TBC*).

### 2022-07-27 paper/manuscript.tex
add additional analysis for dynamics difference
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

>>>>

\hypertarget{additional-analysis-for-dynamics-difference}{%
\section{Additional analysis for dynamics difference}\label{additional-analysis-for-dynamics-difference}}

\hypertarget{experiment-1-4}{%
\subsection{Experiment 1}\label{experiment-1-4}}

A two-way repeated-measures ANOVA with the factors Condition (teaching vs.~performing) and Transition Type (FtoP vs.~PtoF) showed that there was a significant main effect of Transition Type (\emph{F}(1,30) = 741, \emph{p} \textless{} 0.001, \(\eta_G^2\) = 0.88) and a significant interaction between Condition and Transition Type (\emph{F}(1,30) = 7.87, \emph{p} = 0.009, \(\eta_G^2\) = 0.009, \emph{Fig TBC}). Post-hoc comparisons based on the estimated marginal means with Tukey adjustment showed that there was no significant difference when changing from forte to piano (\emph{p} = 0.085) and from piano to forte (\emph{p} = 0.075) between the teaching condition {[}FtoP: \emph{M} = -0.62, \emph{SD} = 0.24, PtoF: \emph{M} = 1.10, \emph{SD} = 0.34{]} and the performing condition {[}FtoP: \emph{M} = -0.56, \emph{SD} = 0.25, PtoF: \emph{M} = 1.03, \emph{SD} = 0.40{]}.

\hypertarget{experiment-2-4}{%
\subsection{Experiment 2}\label{experiment-2-4}}

A two-way repeated-measures ANOVA with the factors Condition (teaching vs.~performing) and Transition Type (FtoP vs.~PtoF) showed that there was a significant main effect of Transition Type (\emph{F}(1,19) = 42, \emph{p} \textless{} 0.001, \(\eta_G^2\) = 0.63). However, there was no significant interaction between Condition and Transition Type (\emph{F}(1,19) = 1.10, \emph{p} = 0.306, \(\eta_G^2\) = 0.008, \emph{Fig TBC}).
